Risk Perceptions for Wearable Devices

### 2015-01-08 wearables_survey.tex
wordsmithing on page1,2

\maketitle
\begin{abstract}
We performed an online survey to examine risk perceptions surrounding wearable computing devices. We examine different data types that might be captured,  and the effect of who the data is shared with. We surveyed 1,784 participants about 72 data types and 4 data recipients to quantify risk perceptions across a wide range of scenarios, and evaluate of which factors contribute to the severity of these risks. Following previous work, we also asked participants to perform a risk/benefit analysis comparing 20 new technologies with other well-established technologies. The results of this study can be used to guide future research in wearable device security, especially research that helps to protect sensitive data and guides the design of effective privacy notifications and indicators.
\end{abstract}

@@

Wearable devices bring with them some new potential security and privacy concerns. Many of these concerns relate to users' activities being exposed to the public without their awareness or consent. For instance, Fitbit's fitness profiles were public by default and also allowed users to track sex as an exercise~\cite{Fitbit}, resulting in the inadvertent disclosure of sensitive user information. In other instances, public discomfort prevented companies from enabling certain capabilities; Google Glass apps are prohibited from using facial recognition to mitigate potential privacy concerns~\cite{GlassDetection}.

To avoid scandalous breaches of privacy and public opposition to new capabilities, it is critical that we understand user concerns surrounding wearable devices before wearables become increasingly ubiquitous and powerful~\cite{Implants}. A better understanding of users' risk perceptions will enable researchers and companies to focus on users' greatest concerns. The goal of this paper is to gain a better sense of what those concerns might be.

@@

Our survey contained two main sections.
In one section, we presented participants with several scenarios---something undesirable that might happen with their wearable device---and asked them to rate their level of concern if each scenario were to happen.
This was intended to elicit their perception of the severity of the impact of the risk.
In the other section, we asked participants to compare the risks and benefits of wearable technologies to better understood technologies, following the same methodology as a seminal study in risk perception from Fischhoff \etal \cite{Fischhoff}.
Our survey design is based on two prior risk perception studies, as we describe next.

@@

\begin{packed_item}
\item Your work contacts
\item Your friends
\item The public
\item The app's server (but didn't share it with anyone else)
\end{packed_item}

>>>>

\maketitle
\begin{abstract}
We performed an online survey to examine risk perceptions surrounding wearable computing devices. We examine different data types that might be captured,  and the effect of who the data is shared with. We surveyed 1,784 participants about 88 data types and 4 data recipients to quantify risk perceptions across a wide range of scenarios, and evaluate of which factors contribute to the severity of these risks. Following previous work, we also asked participants to perform a risk/benefit analysis of 20 new technologies along with other well-understood technologies. The results of this study can be used to guide future research in wearable device security, especially research that helps protect sensitive data and design effective privacy notifications or indicators.
\end{abstract}

@@

Wearable devices bring with them new potential security and privacy concerns. Many of these concerns relate to users' activities being exposed to the public without their awareness or consent. For instance, Fitbit's fitness profiles were public by default and also allowed users to track sex as an exercise~\cite{Fitbit}, resulting in the inadvertent disclosure of sensitive user information. In other instances, public discomfort prevented companies from enabling certain capabilities; Google Glass apps are prohibited from using facial recognition to mitigate potential privacy concerns~\cite{GlassDetection}.

To avoid scandalous breaches of privacy and public opposition to new capabilities, it is critical we understand user concerns surrounding wearable devices before wearables become increasingly powerful and ubiquitous~\cite{Implants}. A better understanding of users' risk perceptions will enable researchers and companies to focus on users' greatest concerns. The goal of this paper is to gain a better sense of what those concerns might be.

@@

Our survey contained two main sections.
In one section, we presented participants with several scenarios---something undesirable that might happen with their wearable device---and asked them to rate their level of concern if each scenario were to happen.
This was intended to elicit their perception of the severity and impact of the risk.
In the other section, we asked participants to compare the risks and benefits of wearable technologies to better understood technologies, following the same methodology as a seminal study in risk perception by Fischhoff \etal \cite{Fischhoff}.
Our survey design is based on two prior risk perception studies, as we describe next.

@@

\begin{packed_item}
\item Your work contacts
\item Your friends
\item The public
\item The app's server (but didn't share it with anyone else)\\[-.8cm]
\end{packed_item}
